### 2017-01-17 Projects/DelCo_2012/Report/DelCo_2012.tex
Updated month/year on title pages

\vspace*{2\baselineskip}
December 2016}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1927 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (December 2016) \\
CODEN: NTNOEF }

>>>>

\vspace*{2\baselineskip}
January 2017}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1927 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (January 2017) \\
CODEN: NTNOEF }
